\renewcommand{\abstractname}{Acknowledgments}
\begin{abstract}
This thesis, and the obtained project results would not have been possible without help from student colleagues, friends and support from the Department of Engineering Cybernetics. 

I would first like to thank my project supervisor, Professor Tor Onshus of the Department of Engineering Cybernetics at NTNU, for allowing me to work on such an open and interesting topic, and for providing valuable advice and guidance through the two last semesters. He has been quick to respond to problems with the project, and gave me with a sense of urgency when the project was lagging far behind schedule in march.

Among my student colleagues, Eirik Wold Solnør, Vegard Blomseth Johnsen and Henrik Rudi Haave have been particularly helpful during testing sessions. Over the last two semesters, Ole Magnus Siqveland and I have used the same robot platform for our projects. Through collaboration, we found a hardware setup that worked for both of us; a new shelf structure with compartments for the various hardware components.

I would like to thank the foreman, Terje Haugen, and apprentice Daniel Bogen at the mechanical workshop for building the new compartments and frames for the robot used in this thesis. Many thanks goes to the employees at the electronics workshop for allowing me to borrow tools and equipment, and providing some hints and tips. 

I am very grateful to my parents and Andrea Myklebust for supporting me through the years at NTNU. Thank you!

Sincerely,
Vegard Stjerna Lindrup


\end{abstract}