\begin{titlingpage}

\noindent
\begin{tabular}{@{}p{4cm}l}
\textbf{Title:} 	& \thetitle \\
\textbf{Student:}	& \theauthor \\
\end{tabular}

\vspace{4ex}
\noindent\textbf{Problem description:}
\vspace{2ex}

The goal of this thesis is to identify how an autonomous and remotely operated robot can utilize visual sensors. This project is a continuation of several projects on the topic of robotic maintenance. Therefore, the sensor applications should focus on maintenance tasks and movement of the mobile robot. The thesis should build upon the preceding project on this topic, which looked at depth perception for obstruction detection. To complete this goal, the student should:

\begin{enumerate}
	\item	Gain knowledge on theory, implementations and solutions for robotic maintenance and mobile autonomous robots that are relevant for this topic.
	\item	Present a set of development tools and hardware that are suitable in light of the goal above. 
	\item	Propose a test platform for demonstrating some selected tasks performed by using vision based sensors. This platform may be based the existing mobile platform from the preceding project, either in its original or a modified form.
	\item	Develop solutions to at least one task that an autonomous maintenance robot could face, e.g. pick up an object, move to dock, or visual inspection. The solution must use a vision-based sensor to solve the task.
	\item	Assess the performance of the solution, and suggest improvements for the future.
\end{enumerate}


\vspace{6ex}

\noindent
\begin{tabular}{@{}p{4cm}l}
\textbf{Responsible professor:} 	& \theprofessor \\
%\textbf{Supervisor:}			& \thesupervisor \\
\end{tabular}

\end{titlingpage}